Towards a Formally Verified EVM in Production Environment

### 2020-04-28 final-3/paper.tex
paper update

OCaml is a functional programming language where the programs can be compiled either to OCaml bytecode or executable binaries. 
In the latter case, a runtime library is attached to handle various non-functional features like memory management. 
Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface
in static or dynamic linking. 
So we first defined a series of customized drivers to extract WhyML programs into OCaml programs. 
After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library. 
This library can be further called by the EVM host in Rust.

@@

>>>>

OCaml is a functional programming language that shares a highly identical language definition and formal semantics with Why3. 
Through the official OCaml code generator equipped with Why3, 
we extract the verified specification of EVM into an executable OCaml module. 
A JSON-based protocol is developed as a bridge between the OCaml implementation and the EVM host in Rust.

% OCaml is a functional programming language where the programs can be compiled either to OCaml bytecode or executable binaries. 
% In the latter case, a runtime library is attached to handle various non-functional features like memory management. 
% Through the \texttt{Callback} module, OCaml allows us to register a set of callback functions which can be used as an interface
% in static or dynamic linking. 
% So we first defined a series of customized drivers to extract WhyML programs into OCaml programs. 
% After the extraction, the OCaml implementation of EVM is then encapsulated and exposed as a static linked library. 
% This library can be further called by the EVM host in Rust.

@@

\paragraph{Testing of arithematic operations.}
Cita-vm~\cite{citavm} is an Rust implementation of the Ethereum Virtual Machine developed by the CITAHub team. 
In a forked version of Cita-vm, we patched the EVM interpreter by redirecting it to the OCaml implementation. 
From the official EVM Consensus Tests~\cite{evmtests},
we select the \emph{vmArithmeticTest} set and run the test cases. 
The OCaml EVM implementation passes all the selected test cases and 
proves its capability in the production environment.
A guide of reproducing the test result can be found at \cite{Examples}.
